Number recognition for use in a Sudoku solver

### 2012-03-15 doc/icml2010stylefiles/paper.tex
- fixed/improved svm grid search
- added grid search result plotting

\section{Training}
\subsection{Neural Network}
\begin{figure}[ht]
	\centerline{\includegraphics[width=\columnwidth, trim=0 30 0 30]{nn}}
	\caption{Neural Network with one hidden layer}
	\label{fig:nn}
\end{figure}
\subsection{Support Vector Machines}
The next technique we applied to the discussed problem are Support Vector Machines \cite{Bishop200608} which try to solve the following optimization problem:
\begin{align*}
\min_{w,b} &~~ \frac{1}{2}||w||^2 + C \sum_{i=1}^{n} \xi_i\\
\text{subject to } &~~ y_i(w^T \phi(x_i) + b) - 1 + \xi_i \ge 0\\
\text{and} &~~ \xi_i \ge 0.
\end{align*}
Using a radial basis function (RBF) as kernel we performed a grid search over $C$ and $\gamma$ to find those parameters that provide the highest accuracy on the validation set. We used the open source library ``libsvm'' \cite{chang2011libsvm} wrapped by some octave scripts for setting up data sets and performing the grid search.
\subsection{Logistic Regression}

>>>>

\section{Training}
\subsection{Neural Network}
\begin{figure}[ht]
	\centerline{\includegraphics[width=\columnwidth, trim=0 30 0 30]{nn}}
	\caption{Neural Network with one hidden layer}
	\label{fig:nn}
\end{figure}
\subsection{Support Vector Machines}
The next technique we applied to the discussed problem are Support Vector Machines \cite{Bishop200608} which try to solve the following optimization problem:
\begin{align*}
\min_{w,b} &~~ \frac{1}{2}||w||^2 + C \sum_{i=1}^{n} \xi_i\\
\text{subject to } &~~ y_i(w^T \phi(x_i) + b) - 1 + \xi_i \ge 0\\
\text{and} &~~ \xi_i \ge 0.
\end{align*}
Using a radial basis function (RBF) as kernel we performed a grid search over $C$ and $\gamma$ to find those parameters that provide the highest accuracy on the test set. We used the open source library ``libsvm'' \cite{chang2011libsvm} wrapped by some octave scripts for setting up data sets and performing the grid search with k-fold cross validation. Grid search with cross validation resulted in accuracies illustrated in \ref{fig:svm_grid_search}, thus we chose $C = ?$ and $\lambda = ?$.
\begin{figure}[ht]
	\centerline{\includegraphics[scale=0.20, trim=0 0 10 0]{gridSearchSVMPlot}}
	\caption{}
	\label{fig:svm_grid_search}
\end{figure}

\subsection{Logistic Regression}

\color{red}performance on an example sudoku\color{black}
